Trans-Dimensional Bayesian Inference for Gravitational Lens Substructures

### 2015-09-01 Papers/ms.tex
More sensible image names

\section{{\revisions``Easy''} Simulated Data}
To demonstrate the method, we generated a simulated dataset {\revisions where
the lens was an SIE$+\gamma$ profile with a single additional substructure}.
The image is shown in Figure~\ref{fig:simulated_image}, and
consists of 100 $\times$ 100 pixels. The point spread function (PSF) was compact and was
defined on a 5 $\times$ 5 grid. The data was created by firing only one ray
per pixel, and the inference was also carried out under the same level of
approximation. Since the model assumptions are all correct for this image, the
demonstration here is purely to illustrate the computational tractability of
the problem, and the kind of outputs the method can produce.

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{simulated_image.pdf}
\caption{A simulated image of a simple ``galaxy'' lensed by an SIE+$\gamma$
lens in the center of the image (which does not contribute any flux), plus a
single substructure close to the top left image.
The image was blurred by a PSF and had some noise added.\label{fig:simulated_image}}
\end{center}
\end{figure}

@@

\section{The Cosmic Horseshoe}
As a further demonstration the method, we apply it to the g-band data
of the Cosmic Horseshoe J1004+4112 \citep{belokurov, 2008MNRAS.388..384D} taken with the Isaac Newton Telescope (INT). The image is shown in Figure~\ref{fig:horseshoe_image}.
For this system,
more data is available (i and U band data, as well as more recent
Hubble Space Telescope (HST) imaging), although the g-band image is the highest
signal-to-noise of the INT images. The source redshift is $z_s=2.379$, and the
lens is a massive luminous red galaxy at $z_l=0.4457$.
Unfortunately our current implementation
doesn't allow for multi-band data (unlike \citet{2011MNRAS.412.2521B}), and
is quite slow when running on the larger HST image. Therefore this section
should be considered a further demonstration of the technique, and not a
thorough study of this system.

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{horseshoe_image.pdf}
\caption{The g-band INT image of the Cosmic Horseshoe, with the lens galaxy
subtracted.
\label{fig:horseshoe_image}}
\end{center}
\end{figure}

>>>>

\section{{\revisions``Easy''} Simulated Data}
To demonstrate the method, we generated a simulated dataset {\revisions where
the lens was an SIE$+\gamma$ profile with a single additional substructure}.
The image is shown in Figure~\ref{fig:image1}, and
consists of 100 $\times$ 100 pixels. The point spread function (PSF) was compact and was
defined on a 5 $\times$ 5 grid. The data was created by firing only one ray
per pixel, and the inference was also carried out under the same level of
approximation. Since the model assumptions are all correct for this image, the
demonstration here is purely to illustrate the computational tractability of
the problem, and the kind of outputs the method can produce.

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{image1.pdf}
\caption{A simulated image of a simple ``galaxy'' lensed by an SIE+$\gamma$
lens in the center of the image (which does not contribute any flux), plus a
single substructure close to the top left image.
The image was blurred by a PSF and had some noise added.\label{fig:image1}}
\end{center}
\end{figure}

@@

\section{The Cosmic Horseshoe}
As a further demonstration the method, we apply it to the g-band data
of the Cosmic Horseshoe J1004+4112 \citep{belokurov, 2008MNRAS.388..384D} taken with the Isaac Newton Telescope (INT). The image is shown in Figure~\ref{fig:image3}.
For this system,
more data is available (i and U band data, as well as more recent
Hubble Space Telescope (HST) imaging), although the g-band image is the highest
signal-to-noise of the INT images. The source redshift is $z_s=2.379$, and the
lens is a massive luminous red galaxy at $z_l=0.4457$.
Unfortunately our current implementation
doesn't allow for multi-band data (unlike \citet{2011MNRAS.412.2521B}), and
is quite slow when running on the larger HST image. Therefore this section
should be considered a further demonstration of the technique, and not a
thorough study of this system.

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{image3.pdf}
\caption{The g-band INT image of the Cosmic Horseshoe, with the lens galaxy
subtracted.
\label{fig:image3}}
\end{center}
\end{figure}
